Supplement to: Library Learning for Neurally-Guided Bayesian Program Induction

### 2018-12-16 spotlight.tex
3-panel figure

@@

\begin{frame}{Library Learning}
\centering
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
\begin{tabular}{cc}
    \toprule
Tasks and     \pop{Programs} & DSL\\
    \midrule
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 2\, 3]}$\to$\code{[7\, 3]}         \\
          \code{[1\, 2\, 3\, 4]}$\to$\code{[3\, 4]} \\
          \code{[4\, 3\, 2\, 1]}$\to$\code{[4\, 3]} \\
          \pop{\code{$f(\ell) = $}\code{($f_1$ $\ell$ ($\lambda$ (x)}}\\
          \hspace{1.15cm}\pop{\code{(> x 2)))}}       \\
          \\
          \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \pop{\code{$f(\ell) = $}\code{($f_2$ $\ell$)}}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \pop{\code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}}
        \end{tabular}
      \end{tabular}
    &
    \begin{tabular}{l}
      \popp{$f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}}\\
      \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
      \popp{$f_1(\ell,$\code{p}$) \,=\, $\code{(foldr $\ell$ nil ($\lambda$ (x a)}}\\
      \hspace{0.5cm}\popp{\code{(if (p x) (cons x a) a)))}}\\
      \hspace{\helpSize}($f_1$: \emph{Higher-order filter function})\\
      %(lambda (fold $0 0 (lambda (lambda (if (gt? $0 $1) $0 $1)))))
      \popp{$f_2(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}}\\
      \popp{\phantom{$f_2(\ell) \,=\, $}\code{(if (> a x) a x)))}}\\
      \hspace{\helpSize}($f_2$: \emph{Maximum element in list $\ell$})\\
      \popp{$f_3(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}}\\
      \phantom{$f_1(\ell,$}
      \popp{\code{($\lambda$ (x a) (if a a (= k x))))}}\\
      \hspace{\helpSize}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
    \end{tabular}
  \\\bottomrule
  \end{tabular}
  \begin{itemize}
  \item Learned DSL primitives can call each other
    \item Rediscovers higher-order functions like \code{filter}
    \end{itemize}
\end{frame}

\newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}

\begin{minipage}[c]{0.6\textwidth}
  \visible<2->{  \begin{tikzpicture}[scale=0.8,line width=0.5mm]
      \node at (2,1) {\underline{\textbf{Explore}: Infer programs, fixing DSL and neural net}};
      \begin{scope}[shift = {(-3,0)}]
    \node at (0,0) (d){DSL};
    \node at ([yshift = -2cm]d) (t){$\text{Task}$};

    \node at ([xshift = 2cm]t) (nn){
      \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.2,shift={+(-1,2.5)}}]
        \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
        \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
        \node[rectangle] at (1,1) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (I-\name) at (0,-\y) {};
        \foreach \name / \y in {1,...,3}
            \node[neuron] (H-\name) at (1,-\y-0.5) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (O-\name) at (2,-\y) {};
        \foreach \source in {1,...,4}
            \foreach \dest in {1,...,3}
                \draw [-latex] (I-\source) -- (H-\dest);
        \foreach \source in {1,...,3}
            \foreach \dest in {1,...,4}
                \draw [-latex] (H-\source) -- (O-\dest);
      \end{tikzpicture}
    };
    \node[align = center, text width = 1cm] at ([yshift = 0.9cm,xshift=-0.5cm]nn.north) {\baselineskip=0pt \small Recog. model\par};
    \draw [red,-{>[scale=0.2]}] (t.east) -- ([xshift = -0.5cm]nn.west);

    \node[draw,rounded corners, inner sep = 10] at ([xshift = 4.2cm,yshift = -1cm]) (s){Search};

@@

    \node[align=left] at ([xshift=2cm]s.east) (f) {Programs};
    \draw [->  ] (s.east) -- (f.west);

    \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
      \end{scope}
      \visible<5->{
        \node(repeat)[scale=8] at (6,-3.5) {$\circlearrowleft$};
        \node at (repeat) {\emph{Repeat!}};
      }
  \end{tikzpicture}}

  \vspace{-1.5cm}

\visible<3->{  \begin{tikzpicture}[scale=0.4,line width=0.5mm]
    \node at (0,0) (f1){progs. for task$_1$};
    \node at ([yshift = -1.4cm]f1.south) (f2){progs. for task$_2$};
    \node at ([yshift = -1.4cm,xshift=1.5cm]f2.south) (f3){DSL};

    \node(c)[rectangle, rounded corners, draw, minimum width = 3cm, minimum height = 2.5cm, anchor = north west] at (5.2,1) {};
%    \node[anchor=north] at (c.north) {Compression};
    \node at ([yshift=1cm,xshift=-3cm]c.north) {\underline{\textbf{Compress}: Update DSL, fixing programs}};
    \draw [-> ] (f1.east) -- (c.west|-f1.east);
    \draw [-> ] (f2.east) -- (c.west|-f2.east);
    \draw [-> ] (f3.east) -- (c.west|-f3.east);

    \node[right](d) at ([xshift = 1.6cm,yshift = -0.0cm]c.east) {
      \begin{tikzpicture}[scale=0.6]
        \node[align=center] at (0,0) {DSL+};
\begin{scope}[shift={(0.6,-0.5)}]
  \node[pop3](p1) at (-1,-1) {\code{+}};
  \node[pop3](n1) at (0.6,-0.9) {\code{1}};
  \node[pop3](a) at (0,-1) {\code{ }};
  \draw[pop3] (0,0) -- (p1.north);
  \draw[pop3] (0,0) -- (n1.north);
  \draw[pop3] (-0.3,-0.3) -- (a.north);
  \end{scope}
        \end{tikzpicture}
      };
    \draw [-> ] (c.east) -- (d.west);

    \node at (c.center) {
\begin{tikzpicture}[scale=0.6]

@@

  \begin{scope}[shift={(0.9,-1.3)}]
      \node(l1) at (0,0) {};
  \node[color=pop3](p1) at (-1,-1) {\code{+}};
  \node[color=pop3](n1) at (0.7,-0.9) {\code{1}};
  %\node(x1) at (0,-1) {};
  \draw[color=pop3] (l1.south) -- (p1.north);
  \draw[color=pop3] (l1.south) -- (n1.north);
  \draw[color=pop3] (-0.5,-0.45) -- (0,-1);

@@

    \end{tikzpicture}}

\end{minipage}%
\begin{minipage}[c]{0.28\textwidth}
  \vspace{-1cm}
  \begin{tikzpicture}[scale=1,line width=0.5mm]

>>>>

  \end{frame}
\begin{frame}{Library learning}

  \centering
\Large
  \begin{tabular}{c}
              \code{[7\, 2\, 3]}$\to$\code{[7\, 3]}         \\
          \code{[1\, 2\, 3\, 4]}$\to$\code{[3\, 4]} \\
          \code{[4\, 3\, 2\, 1]}$\to$\code{[4\, 3]} \\\\
          \visible<3->{
          \code{$f(\ell) = $}\code{($f_1$ $\ell$ ($\lambda$ (x) (> x 2)))}}
  \end{tabular}
  \vspace{2cm}

  \visible<2->{
    \textbf{Library:}\\
          $f_1(\ell,$\code{p}$) \,=\, $\code{(foldr $\ell$ nil ($\lambda$ (x a) (if (p x) (cons x a) a)))}\\
    \hspace{\helpSize}($f_1$: \emph{Higher-order filter function})\\
    \hspace{\helpSize}(\emph{Get elements} $x$ \emph{ from $\ell$ where \code{(p $x$)} returns true})
    }

@@

\begin{frame}{Subset of 38 learned library routines for list processing}
  \Large\centering
  \begin{tabular}{ll}
    \begin{tabular}{l}
            $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}
      \end{tabular}&$f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$}\\\\
    \begin{tabular}{l}
      $f_1(\ell,$\code{p}$) \,=\, $\code{(foldr $\ell$ nil ($\lambda$ (x a)}\\
  \hspace{0.5cm}\code{(if (p x) (cons x a) a)))}
      \end{tabular}&    
$f_1$: \emph{Higher-order filter function}\\\\
    \begin{tabular}{l}
      $f_2(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\
\phantom{$f_2(\ell) \,=\, $}\code{(if (> a x) a x)))}
      \end{tabular}
&$f_2$: \emph{Maximum element in list $\ell$}\\\\
    \begin{tabular}{l}
      $f_3(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}\\
      \phantom{$f_1(\ell,$}
\code{($\lambda$ (x a) (if a a (= k x))))}
      \end{tabular}
&$f_2$: \emph{Whether $\ell$ contains }\code{k}
    \end{tabular}
  \end{frame}

\begin{frame}{Explore/Compress/Compile as Bayesian Inference}

\centering

  \begin{tikzpicture}[scale=1,line width=0.5mm]

  \node[latent,scale=1] at (3.5,3) (dx){DSL};
  \node[latent,scale=1] at ([yshift=-1.5cm,xshift=2cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-1.45cm]zp) (xp) {task};
  \node[latent,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);

  \node[latent,scale=1] at ([xshift=-2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=-2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);

  \draw [->] (dx.south) -- (zp.north);
  \draw [->] (zp.south) -- (xp.north);

  \end{tikzpicture}
\end{frame}
\begin{frame}{Explore/Compress/Compile as {\color{red}Amortized} Bayesian Inference}\centering

\newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}
\begin{tikzpicture}[scale=1,line width=0.5mm]

  \draw [->,red] ([xshift=2cm]dx.east) -- ([xshift=3cm]dx.east);
  \node at ([xshift=3.2cm]dx.east]) (uses){is};k
  \node at ([xshift=0.5cm]uses.east) (nnn){\NeuralNetwork{0.17}};
  \draw[thin] ([xshift=1.9cm,yshift=0.4cm]dx.east) rectangle
  ([xshift=0.5cm,yshift=-0.3cm]nnn.south);
  \end{tikzpicture}
\end{frame}

\begin{frame}{\underline{\textbf{Explore}}/Compress/Compile as {\color{red}Amortized} Bayesian Inference}\centering
  \underline{\textbf{Explore}: Infer programs, fixing DSL and neural recognition model}\vspace{1cm}

\newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}
\begin{tikzpicture}[scale=1,line width=0.5mm]

  \node[obs,scale=1] at (3.5,3) (dx){DSL};
  \node[latent,scale=1] at ([yshift=-1.5cm,xshift=2cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-1.45cm]zp) (xp) {task};
  \node[latent,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \draw [->,red] ([xshift=2cm]dx.east) -- ([xshift=3cm]dx.east);
  \node at ([xshift=3.2cm]dx.east]) (uses){is};k
  \node at ([xshift=0.5cm]uses.east) (nnn){\NeuralNetwork{0.17}};
  \draw[thin] ([xshift=1.9cm,yshift=0.4cm]dx.east) rectangle
  ([xshift=0.5cm,yshift=-0.3cm]nnn.south);
  \end{tikzpicture}
  \end{frame}

\begin{frame}{\underline{\textbf{Explore}}/Compress/Compile as {\color{red}Amortized} Bayesian Inference}\centering
  \underline{\textbf{Explore}: Infer programs, fixing DSL and neural recognition model}%

%  \vspace{1cm}

    \begin{tikzpicture}[scale=1.2,line width=0.5mm]

      \begin{scope}[shift = {(-3,0)}]
        \node[align=right] at (0,0) (d){\textbf{DSL}\\
        $f_1$, $f_2$, ...};
    \node[align=center] at ([yshift = -2cm]d) (t){\textbf{Task}\\
      \footnotesize            \code{[7\, 2\, 3]}$\to$\code{[7\, 3]}         \\
      \footnotesize    \code{[1\, 2\, 3\, 4]}$\to$\code{[3\, 4]} \\
      \footnotesize    \code{[4\, 3\, 2\, 1]}$\to$\code{[4\, 3]} };

    \node at ([xshift = 1.3cm]t.east) (nn){
      \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.2,shift={+(-1,2.5)}}]
        \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
        \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
        \node[rectangle] at (1,1) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (I-\name) at (0,-\y) {};
        \foreach \name / \y in {1,...,3}
            \node[neuron] (H-\name) at (1,-\y-0.5) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (O-\name) at (2,-\y) {};
        \foreach \source in {1,...,4}
            \foreach \dest in {1,...,3}
                \draw [-latex] (I-\source) -- (H-\dest);
        \foreach \source in {1,...,3}
            \foreach \dest in {1,...,4}
                \draw [-latex] (H-\source) -- (O-\dest);
      \end{tikzpicture}
    };
    \node[align = center, text width = 1cm] at ([yshift = 0.5cm,xshift=0cm]nn.north) {\baselineskip=0pt \small Recog. model\par};
    \draw [red,-{>[scale=0.2]}] (t.east) -- ([xshift = -0.5cm]nn.west);

    \node[draw,rounded corners, align=center, inner sep = 10] at ([xshift = 4.2cm,yshift = 1cm]t.east) (s){Neurally-Guided\\ Enumerative Search};

@@

    \node[align=left] at ([xshift=3cm]s.east) (f) {\textbf{Programs:}\\
\small    \code{($f_1$ $\ell$ ($\lambda$ (x) (> x 2)))}};
    \draw [->  ] (s.east) -- (f.west);

    \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
      \end{scope}

      \node at ([yshift=-2.8cm,xshift=-0.5cm]f.south) {
  \newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}
\begin{tikzpicture}[scale=0.8,line width=0.25mm]

  \node[obs,scale=1] at (3.5,3) (dx){DSL};
  \node[latent,scale=1] at ([yshift=-1.5cm,xshift=2cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-1.45cm]zp) (xp) {task};
  \node[latent,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \draw [->,red] ([xshift=2cm]dx.east) -- ([xshift=3cm]dx.east);
  \node at ([xshift=3.2cm]dx.east]) (uses){is};k
  \node at ([xshift=0.5cm]uses.east) (nnn){\NeuralNetwork{0.12}};
  \draw[thin] ([xshift=1.9cm,yshift=0.4cm]dx.east) rectangle
  ([xshift=0.5cm,yshift=-0.3cm]nnn.south);
  \end{tikzpicture}
      };
  \end{tikzpicture}

\begin{frame}{Explore/\underline{\textbf{Compress}}/Compile as {\color{red}Amortized} Bayesian Inference}\centering
  \underline{\textbf{Compress}: Update DSL, fixing programs}
\vspace{1cm}

\newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}
\begin{tikzpicture}[scale=1,line width=0.5mm]

  \node[latent,scale=1] at (3.5,3) (dx){DSL};
  \node[obs,scale=1] at ([yshift=-1.5cm,xshift=2cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-1.45cm]zp) (xp) {task};
  \node[obs,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \node[obs,scale=1] at ([xshift=-2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=-2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \draw [->,red] ([xshift=2cm]dx.east) -- ([xshift=3cm]dx.east);
  \node at ([xshift=3.2cm]dx.east]) (uses){is};k
  \node at ([xshift=0.5cm]uses.east) (nnn){\NeuralNetwork{0.17}};
  \draw[thin] ([xshift=1.9cm,yshift=0.4cm]dx.east) rectangle
  ([xshift=0.5cm,yshift=-0.3cm]nnn.south);
  \end{tikzpicture}
  \end{frame}

\begin{frame}{Explore/\underline{\textbf{Compress}}/Compile as {\color{red}Amortized} Bayesian Inference}\centering
  \underline{\textbf{Compress}: Update DSL, fixing programs}

  \begin{tikzpicture}[scale=0.4,line width=0.5mm]
    \node at (0,0) (f1){progs. for task$_1$};
    \node at ([yshift = -1.4cm]f1.south) (f2){progs. for task$_2$};
    \node at ([yshift = -1.4cm,xshift=1.5cm]f2.south) (f3){DSL};

    \node(c)[rectangle, rounded corners, draw, minimum width = 8cm, minimum height = 3cm, anchor = north west] at (5.2,1) {};
    \draw [-> ] (f1.east) -- (c.west|-f1.east);
    \draw [-> ] (f2.east) -- (c.west|-f2.east);
    \draw [-> ] (f3.east) -- (c.west|-f3.east);

    \node[right](d) at ([xshift = 1.6cm,yshift = -0.0cm]c.east) {
      \begin{tikzpicture}[scale=0.9,line width=0.5mm]
        \node[align=center] at (0,0) {DSL+};
        \begin{scope}[shift={(0.6,-0.5)}]
          \node[pop3](p1) at (-1,-1) {\code{+}};
          \node[pop3](n1) at (0.6,-0.9) {\code{1}};
          \node[pop3](a) at (0,-1) {\code{ }};
          \draw[pop3] (0,0) -- (p1.north);
          \draw[pop3] (0,0) -- (n1.north);
          \draw[pop3] (-0.3,-0.3) -- (a.north);
        \end{scope}
    \end{tikzpicture}};
    \draw [-> ] (c.east) -- (d.west);

    \node at (c.center) {
\begin{tikzpicture}[scale=1.2,line width=0.5mm]

@@

  \begin{scope}[shift={(3,0.5)}]
      \node(l1) at (0,0) {};
  \node[color=pop3](p1) at (-1,-1) {\code{+}};
  \node[color=pop3](n1) at (0.7,-0.9) {\code{1}};
  %\node(x1) at (0,-1) {};
  \draw[color=pop3] (l1.south) -- (p1.north);
  \draw[color=pop3] (l1.south) -- (n1.north);
  \draw[color=pop3] (-0.5,-0.45) -- (0,-1);

@@

    \node at ([yshift=-5.8cm,xshift=-0.5cm]d.south) {
  \newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}
\begin{tikzpicture}[scale=0.8,line width=0.25mm]

  \node[latent,scale=1] at (3.5,3) (dx){DSL};
  \node[obs,scale=1] at ([yshift=-1.5cm,xshift=2cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-1.45cm]zp) (xp) {task};
  \node[obs,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \node[obs,scale=1] at ([xshift=-2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=-2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \draw [->,red] ([xshift=2cm]dx.east) -- ([xshift=3cm]dx.east);
  \node at ([xshift=3.2cm]dx.east]) (uses){is};
  \node at ([xshift=0.5cm]uses.east) (nnn){\NeuralNetwork{0.12}};
  \draw[thin] ([xshift=1.9cm,yshift=0.4cm]dx.east) rectangle
  ([xshift=0.5cm,yshift=-0.3cm]nnn.south);
  \end{tikzpicture}
      };

  \end{tikzpicture}

\end{frame}
\begin{frame}{Explore/Compress/\underline{\textbf{Compile}} as {\color{red}Amortized} Bayesian Inference}\centering
\underline{\textbf{Compile}: Train {\color{red} recognition model}}
\vspace{1cm}

\newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}
\begin{tikzpicture}[scale=1,line width=0.5mm]

  \node[obs,scale=1] at (3.5,3) (dx){DSL};
  \node[obs,scale=1] at ([yshift=-1.5cm,xshift=2cm]dx) (zp){prog};
  \node[obs,scale=1] at ([yshift=-1.45cm]zp) (xp) {task};
  \node[obs,scale=1] at ([xshift=2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \node[obs,scale=1] at ([xshift=-2cm]zp) (zp1){prog};
  \node[obs,scale=1] at ([xshift=-2cm]xp) (xp1) {task};
  \draw [->] (zp1.south) -- (xp1.north);
  \draw [->] (dx.south) -- (zp1.north);
  \draw [->,red] (xp1.east) to[out = 30,in = -30] node(nn){} (zp1.east);

  \draw [->,red] ([xshift=2cm]dx.east) -- ([xshift=3cm]dx.east);
  \node at ([xshift=3.2cm]dx.east]) (uses){is};k
  \node at ([xshift=0.5cm]uses.east) (nnn){\NeuralNetwork{0.17}};
  \draw[thin] ([xshift=1.9cm,yshift=0.4cm]dx.east) rectangle
  ([xshift=0.5cm,yshift=-0.3cm]nnn.south);
  \end{tikzpicture}
  \end{frame}
\begin{frame}{Explore/Compress/\underline{\textbf{Compile}} as {\color{red}Amortized} Bayesian Inference}\centering
\underline{\textbf{Compile}: Train {\color{red} recognition model}}
\vspace{1cm}

  \newcommand{\NeuralNetwork}[1]{    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=#1,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}}
\hspace{1.5cm}\begin{tikzpicture}[scale=1.2,line width=0.5mm]
            \node[align=center] at (-3,-1) (d){\Large DSL};
      %    \node at ([xshift = 3cm]d.east) (p2){program};
      \node at ([xshift=2.5cm,yshift = 0cm]d.east) (p1){\Large  program};

      \draw[squiggle,-> ] (d.east) -- node[sloped,above]{sample} (p1.west);

      \node at ([xshift = 2.5cm]p1.east) (t1){ \Large  task};

      \draw [-> ] (p1.east) -- node[above]{ run} (t1.west);

      \node(n) at ([yshift=-1.2cm,xshift=1.6cm]p1.south) {
        \NeuralNetwork{0.17}};
      \draw [->,red] (t1.south) to[out = -90,in = 0]  ([xshift=0.4cm]n.east);
      \draw [->,red] ([xshift=-0.4cm]n.west) to[out = -180,in = -70]  ([xshift=-0.25cm,yshift=0.1cm]p1.south);
